A Large-Scale Study of the Use of Eval in R

### 2020-11-26 inst/paper/main.tex
Reorganize sections
LIPICS cs formatting for ECOOP

\documentclass[a4paper,USenglish,cleveref, autoref, thm-restate]{lipics-v2019}
% This is a template for producing LIPIcs articles. 
% See lipics-manual.pdf for further information.
% for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
% for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
% for section-numbered lemmas etc., use "numberwithinsect"
% for enabling cleveref support, use "cleveref"
% for enabling autoref support, use "autoref"
% for anonymousing the authors (e.g. for double-blind review), add "anonymous"
% for enabling thm-restate support, use "thm-restate"

% \graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

@@

\lstset{ %
  columns=flexible,
  captionpos=b,
  frame=single,
  framerule=0pt,
  framexleftmargin=-1mm,
  framexrightmargin=-1mm,
  tabsize=2,
  belowskip=0pt,
  basicstyle=\small\ttfamily,
  backgroundcolor=\color{LightGray},
  emphstyle=\sffamily,
  keywordstyle=\bfseries,
  commentstyle=\color{Gray}\em,
  stringstyle=\color{Gray}
}
\lstdefinestyle{R}{ %
  language=R,
  deletekeywords={new, env, equal, c, runif, trace, args, exp, t, all, get,
    names, is, environment, class, substitute, expression, list, null, Internal,
    sample, diag, length, rep, nrow, stop, offset, pmax, Machine,
    double, parent, frame, par, methods, end, dir, apply, deparse, missing,
    plot, as, integer, character, inherits, numeric, paste, eval, quote, call,
    formula, df, log, sum, c, local, legend, file, scale, round, title, order,
    drop, which, grid, print, ncol, dim, max, format, sort, rug, matrix, start,
    unique, mean, df, attr, do, power, \$},
  otherkeywords={},
  breaklines=true
}

@@

\newcommand{\eval}{\texttt{eval}\xspace}
\newcommand{\evals}{{\sf eval}s\xspace}
\renewcommand{\parse}{\c{parse}}
\newcommand{\source}{\c{source}}
\newcommand{\local}{\c{local}}
\newcommand{\unlockBinding}{\c{unlockBinding}}
\newcommand{\substitute}{\c{substitute}}
\newcommand{\datatable}{\c{data.table}}
\newcommand{\mlogit}{\c{mlogit}}
\newcommand{\mboost}{\c{mboost}}
\newcommand{\metafor}{\c{metafor}}
\newcommand{\lavaan}{\c{lavaan}}
\newcommand{\mclust}{\c{mclust}}
\newcommand{\gamlss}{\c{gamlss}}
\newcommand{\ggproto}{\c{ggproto}}
\newcommand{\ggplot}{\c{ggplot2}}
\newcommand{\base}{\c{base}}
\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}
\newcommand{\evil}{\emph{evil}\xspace}
\newcommand{\instrumentr}{\emph{instrumentr}\xspace}
\newcommand{\rdyntrace}{\emph{R-dyntrace}\xspace}
\newcommand{\covr}{\emph{covr}\xspace}
\newcommand{\runr}{\emph{runr}\xspace}

\bibliographystyle{plainurl}

\title{A Large-Scale Study of the Use of Eval in R}

%\author{Aviral Goel}{Northeastern University, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{goel.aviral@gmail.com}{https://orcid.org/0000-0002-0814-5015}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional

%\author{Joan R. Public\footnote{Optional footnote, e.g. to mark corresponding author}}{Department of Informatics, Dummy College, [optional: Address], Country}{joanrpublic@dummycollege.org}{[orcid]}{[funding]}

\authorrunning{J.\,Q. Public and J.\,R. Public} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{Aviral Goel, Pierre Donat-Bouillud, Filip Křikava, Christoph Kirsch and Jan Vitek}
% TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10011007.10011006.10011050.10010517</concept_id>
  <concept_desc>Software and its engineering~Scripting languages</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10002944.10011123.10010912</concept_id>
  <concept_desc>General and reference~Empirical studies</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10011007.10011006.10011008</concept_id>
  <concept_desc>Software and its engineering~General programming languages</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Scripting languages}
\ccsdesc[500]{General and reference~Empirical studies}
\ccsdesc[500]{Software and its engineering~General programming languages}

\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords

\category{} %optional, e.g. invited paper

\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversion{A full version of the paper is available at \url{...}.}

\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

\acknowledgements{I want to thank \dots}%optional

%\nolinenumbers %uncomment to disable line numbering

%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

\documentclass[USenglish,cleveref, autoref, thm-restate]{lipics-v2019}

@@

\lstset{ %
  columns=flexible,
  captionpos=b,
  frame=single,
  framerule=0pt,
  framexleftmargin=-1mm,
  framexrightmargin=-1mm,
  tabsize=2,
  belowskip=0pt,
  basicstyle=\small\ttfamily,
  backgroundcolor=\color{LightGray},
  emphstyle=\sffamily,
  keywordstyle=\bfseries,
  commentstyle=\color{Gray}\em,
  stringstyle=\color{Gray}
}
\lstdefinestyle{R}{ %
  language=R,
  deletekeywords={new, env, equal, c, runif, trace, args, exp, t, all, get,
    names, is, environment, class, substitute, expression, list, null, Internal,
    sample, diag, length, rep, nrow, stop, offset, pmax, Machine,
    double, parent, frame, par, methods, end, dir, apply, deparse, missing,
    plot, as, integer, character, inherits, numeric, paste, eval, quote, call,
    formula, df, log, sum, c, local, legend, file, scale, round, title, order,
    drop, which, grid, print, ncol, dim, max, format, sort, rug, matrix, start,
    unique, mean, df, attr, do, power},
  otherkeywords={},
  breaklines=true
}

@@

\newcommand{\eval}{\texttt{eval}\xspace}
\newcommand{\evals}{{\sf eval}s\xspace}
\renewcommand{\parse}{\c{parse}}
\newcommand{\source}{\c{source}}
\newcommand{\local}{\c{local}}
\newcommand{\unlockBinding}{\c{unlockBinding}}
\newcommand{\substitute}{\c{substitute}}
\newcommand{\datatable}{\c{data.table}}
\newcommand{\mlogit}{\c{mlogit}}
\newcommand{\mboost}{\c{mboost}}
\newcommand{\metafor}{\c{metafor}}
\newcommand{\lavaan}{\c{lavaan}}
\newcommand{\mclust}{\c{mclust}}
\newcommand{\gamlss}{\c{gamlss}}
\newcommand{\ggproto}{\c{ggproto}}
\newcommand{\ggplot}{\c{ggplot2}}
\newcommand{\base}{\c{base}}
\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}
\newcommand{\evil}{\emph{evil}\xspace}
\newcommand{\instrumentr}{\emph{instrumentr}\xspace}
\newcommand{\rdyntrace}{\emph{R-dyntrace}\xspace}
\newcommand{\covr}{\emph{covr}\xspace}
\newcommand{\runr}{\emph{runr}\xspace}
\bibliographystyle{plainurl}% the mandatory bibstyle

@@

\title{A Large-Scale Study of the Use of Eval in R}
\titlerunning{Eval in R}

\author{Anon}{Under review}{}{}{}
\authorrunning{Anon}
\ccsdesc[100]{Something}
\Copyright{Anon}
\keywords{R, reflection, eval}

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%\
%%%%%%%                                                                         
\EventEditors{Eds.}
\EventNoEds{2}
\EventLongTitle{European Conference on Object Oriented Programming (ECOOP 2021)}
\EventShortTitle{ECOOP 2021}
\EventAcronym{ECOOP}
\EventYear{2021}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
